Adaptive Scheduling of Scientific Workflows

### 2024-03-07 main.tex
ACM template for icpp. Minor issues with reference format, but otherwise functional

\documentclass{article}

% Language setting
% Replace `english' with e.g. `spanish' to change the document language
\usepackage[english]{babel}

% Set page size and margins
% Replace `letterpaper' with `a4paper' for UK/EU standard size
\usepackage[letterpaper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{algpseudocode}
\usepackage{algorithmicx}
\usepackage{algorithm}

\newcommand{\bottomlevel}[1]{\underline{l}_{#1}} % underline short italic
\newcommand{\criticalpath}{\mathcal{P}}
\newcommand{\parents}[1]{\,\Pi_{#1}}
\newcommand{\children}[1]{\,C_{#1}}
\newcommand{\cluster}{\,\mathcal{S}}
\newcommand{\daghetpart}{\algo{DagHetPart}\xspace}
\newcommand{\dagmem}{\algo{DagHetMem}\xspace}

\title{Dynamic Scheduling }

\begin{document}
    \maketitle

@@

    Then a process similar to Step 4 in \daghetpart can be executed: the newly rearranged blocks are swapped until no
    improvement in makespan can be achieved.

@@

    \section{Interface}

    To trigger a renewed computation of a schedule, the scheduler needs the following informations:
    \begin{itemize}
        \item The timestamp of the change (amount of seconds passed in the system)
        \item Per changed task:
        \begin{itemize}
            \item Task name (and id, if available)
            \item The new runtime
            \item The new memory requirement
        \end{itemize}

        Tasks, for which this information is not delivered are assumed unchanged.
        Previously given information will be used to determine their runtime and memory requirement.
        \item Per changed file transfer (edge in the workflow graph)

        \begin{itemize}
            \item The source and sink task names (to identify the edge)
            \item The new edge weight (size of files transferred)
        \end{itemize}

        \item  Per changed processor:
        \begin{itemize}
            \item Processor name and number (both required, because we have several processors with the same name)
            \item If exited or entered

        Processors, for which no such information is delivered, are assumed to be unchanged.
        Processor exit time is assumed to be the time of the change. This means that all tasks that were scheduled there, have ran.
        However, currently running tasks need to be restarted on another processor and no future tasks cannot be scheduled on the exited processor.
        All task data is assumed to be retrievable from an exited processor without additional time requirements to do so.
    \end{itemize}

    Based on the timestamp, the renewed runtimes of tasks and renewed processor speeds, the scheduler can identify tasks that are finished, running or not started.
    The output of the scheduler is the new schedule: an assignment of each of the (not yet executed) tasks to a processor.

    Assumptions:

    \begin{itemize}
        \item No tasks can disappear, no new tasks can appear during an execution. Same holds for edges.
        \item The processor cannot change characteristics. It can only fail (exit) or appear (enter).

    To be Discussed: The runtime of the scheduler itself is assumed to be zero, for the ease of simulating.

    \bibliographystyle{alpha}
    \bibliography{references}
\end{document}

>>>>

\documentclass[sigconf,review,anonymous]{acmart}
\usepackage{algorithmicx}
\usepackage{amsmath}
\usepackage{graphicx}
%\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{algpseudocode}
\usepackage{algorithm}

%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
    \providecommand\BibTeX{{%
        Bib\TeX}}}

\setcopyright{acmlicensed}
\copyrightyear{2024}
\acmYear{2024}
\acmDOI{XXXXXXX.XXXXXXX}

%% These commands are for a PROCEEDINGS abstract or paper.
\acmConference[ICPP '24]{53rd International Conference on Parallel Processing}{August 12-15, 2024}{Gotland, Sweden}
\acmISBN{978-1-4503-XXXX-X/18/06}

\newcommand{\algo}[1]{\textsc{#1}}
\newcommand{\bottomlevel}[1]{\underline{l}_{#1}} % underline short italic
\newcommand{\criticalpath}{\mathcal{P}}
\newcommand{\parents}[1]{\,\Pi_{#1}}
\newcommand{\children}[1]{\,C_{#1}}
\newcommand{\cluster}{\,\mathcal{S}}
\newcommand{\daghetpart}{\algo{DagHetPart}\xspace}
\newcommand{\dagmem}{\algo{DagHetMem}\xspace}
%%
%% end of the preamble, start of the body of the document source.
\begin{document}

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
    \title{Adaptive Scheduling of Scientific Workflows}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
    \author{Svetlana Kulagina}
    \email{svetlana.kulagina@hu-berlin.de}
    \orcid{0000-0002-2108-9425}
    \affiliation{%
        \institution{Humboldt Universitaet zu Berlin}
        \streetaddress{Unter den Linden 6}
        \city{Berlin}
        \country{Germany}
        \postcode{10099}
    }

       \author{Henning Meyerhenke}
       \affiliation{%
           \institution{Humboldt Universitaet zu Berlin}
           \city{Berlin}
           \country{Germany}
       }
       \email{meyerhenke@hu-berlin.de}

    \author{Anne Benoit}
    \affiliation{%
        \institution{ENS Lyon}
        \city{Lyon}
        \country{France}
    }
    \email{Anne.Benoit@ens-lyon.fr}

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
    \renewcommand{\shortauthors}{Trovato et al.}

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
    \begin{abstract}
       Todo: reinsert CCSXML concepts
    \end{abstract}

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
    \keywords{Scheduling, Adaptive Scheduling, DAG}
    \received{15 April 2024}
    \received[revised]{12 March 2009}
    \received[accepted]{5 June 2009}

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
    \maketitle

    \section{Introduction}

@@

    Then a process similar to Step 4 in %\daghetpart
    can be executed: the newly rearranged blocks are swapped until no
    improvement in makespan can be achieved.

@@

    \bibliographystyle{ACM-Reference-Format}
    \bibliography{references}

\end{document}
\endinput
%%
%% End of file `sample-sigconf.tex'.
